Through the eyes of the teacher

### 2021-01-25 paper_1/paper_1.Rmd

# prepare data (selected from questionnaire data)
quest.raw.data<-read.table("./data/short_questionnaire_data_2101211.txt",sep="\t", header=T)

@@

# create a basic table (tibble) using tidyverse functions
demo.quest.table <- quest.raw.data %>%
  filter(what == "head") %>%
  group_by(group) %>%
  summarise(N=n(),
            "male" = sum(gender),
            "M age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age),
            "sd age" = round(sd(age), 2),
            # "experience" = round(mean(experience), 2) # in order for this to work experience must be turned into integer via as.integer, maybe replace , with .
            )

>>>>

# prepare data (selected from questionnaire data)
quest.raw.data<-read.table("./data/short_questionnaire_data_2101211.txt", dec=",", sep="\t", header=T)

@@

# converting numbers to numeric
raw.data <- raw.data %>%  mutate(experience = as.numeric(as.character(factor(experience))))

# create a basic table (tibble) using tidyverse functions
demo.quest.table <- quest.raw.data %>%
  filter(what == "head") %>%
  group_by(group) %>%
  summarise(N=n(),
            "male" = sum(gender),
            "M age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age),
            "SD age" = round(sd(age), 2),
            "M experience" = round(mean(experience), 2),
            "min experience" = min(experience),
            "max experience" = max(experience),
            "SD experience" = round(sd(experience), 2),
            ) %>%

### 2021-01-25 paper_1/paper_1.tex

\caption{\label{tab:demographicspilot1table,}Demographic Information}

@@

\begin{tabular}{lllllll}
\toprule
group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{male} & \multicolumn{1}{c}{mean age} & \multicolumn{1}{c}{min age} & \multicolumn{1}{c}{max age} & \multicolumn{1}{c}{sd age}\\
\midrule
expert & 2 & 1 & 47.50 & 44 & 51 & 4.95\\
novice & 6 & 2 & 25.67 & 20 & 33 & 4.89\\
\bottomrule
\end{tabular}

>>>>

\caption{\label{tab:demographicspilot1table}Demographic Information and Teaching Experience}

@@

\begin{tabular}{lllllll}
\toprule
group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{male} & \multicolumn{1}{c}{*M* age} & \multicolumn{1}{c}{min age} & \multicolumn{1}{c}{max age} & \multicolumn{1}{c}{sd age}\\
\midrule
expert & 2 & 1 & 47.50 & 44 & 51 & 4.95\\
novice & 6 & 2 & 25.67 & 20 & 33 & 4.89\\
\bottomrule
\end{tabular}
